---
title: "CASE4III"
output: html_document
date: "2024-12-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Step 1: Load and Inspect the Data
```{r}
# Load libraries and data
library(tidyverse)
load("HW4.Rdata")  
ls()  
# Save the matrices to CSV files
write.csv(Liked_M_F, "Liked_M_F.csv", row.names = TRUE)
write.csv(Liked_F_M, "Liked_F_M.csv", row.names = TRUE)
cat("Liked_M_F.csv and Liked_F_M.csv have been created in the current working directory.")
```
Step 2: Compute Correlation Matrices
For Liked_M_F: Correlation between rows (men's preferences for women).
For Liked_F_M: Correlation between rows (women's preferences for men).
```{r}
# Correlations for men and women
cor_m <- apply(Liked_M_F, 1, function(row) cor(t(Liked_M_F), row, use = "pairwise.complete.obs"))
cor_f <- apply(Liked_F_M, 1, function(row) cor(t(Liked_F_M), row, use = "pairwise.complete.obs"))
```
Step 3: Filter Comparison Users
For each target user:
Identify comparison users who have a correlation (ρ) ≥ 0.15 or ≤ -0.15 with the target user.
This ensures we use only diagnostic users (similar or dissimilar).
```{r}
calculate_liking_score <- function(correlations, target_row, liked_matrix) {
  valid_indices <- which(correlations >= 0.15 | correlations <= -0.15)
  if (length(valid_indices) == 0) return(NA)  # Handle missing indices
  rho <- abs(correlations[valid_indices])
  L <- ifelse(correlations[valid_indices] > 0, 
              liked_matrix[valid_indices, target_row], 
              1 - liked_matrix[valid_indices, target_row])
  sum(rho * L, na.rm = TRUE) / sum(rho, na.rm = TRUE)
}
```
Step 4: Calculate Liking Scores
For a target user and a potential partner:
```{r}
# Compute Liking Scores
liking_scores_m <- matrix(NA, nrow = nrow(Liked_M_F), ncol = ncol(Liked_M_F))
liking_scores_f <- matrix(NA, nrow = nrow(Liked_F_M), ncol = ncol(Liked_F_M))

for (i in 1:nrow(Liked_M_F)) {
  for (j in 1:ncol(Liked_M_F)) {
    liking_scores_m[i, j] <- calculate_liking_score(cor_m[i, ], j, Liked_M_F)
    liking_scores_f[j, i] <- calculate_liking_score(cor_f[j, ], i, Liked_F_M)
  }
}
```
Step 5: Calculate Match Scores
For each pair of men and women:

Compute the Match Score as the sum of their Liking Scores:
Match Score = Liking Score (man) + Liking Score (woman)

```{r}

# Compute Match Scores
match_scores <- liking_scores_m + t(liking_scores_f)

# Extract highest Match Scores
match_results <- apply(match_scores, 1, which.max)


```

```{r}
# Compare matches with algorithm
print("Match Results with respect to the 100 candidates:")
print(match_results)

# Print Match Scores for first three men and women
print(match_scores[1:3, 1:3])
```

```{r}

# Extract the submatrix of Match Scores for the first 3 men and 3 women
sub_match_scores <- match_scores[1:3, 1:3]

# Print the submatrix to verify
print("Submatrix of Match Scores (Men 1-3 and Women 1-3):")
print(sub_match_scores)

# Find the best match for each man (row-wise maximum)
row_matches <- apply(sub_match_scores, 1, which.max)
print("Best matches for men (row-wise):")
print(row_matches)  # Columns (women) with the highest scores for each row (man)

# Find the best match for each woman (column-wise maximum)
col_matches <- apply(sub_match_scores, 2, which.max)
print("Best matches for women (column-wise):")
print(col_matches)  # Rows (men) with the highest scores for each column (woman)

# Output the perfect matches
for (i in 1:3) {
  cat(sprintf("Man %d is best matched with Woman %d\n", i, row_matches[i]))
}
for (i in 1:3) {
  cat(sprintf("Woman %d is best matched with Man %d\n", i, col_matches[i]))
}


```